---
title: Blog posts with academic styles 
date: '2017-05-20'
slug: academic-posts
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/global-ecology-and-biogeography.csl
bibliography: ref.bib
---

Goal: I want to write academic style blog posts with: citations, cross-reference of tables and figures, and I want to manage figure path by myself. The default setting of blogdown can handle citations and cross-references pretty well thanks to [Yihui](https://yihui.name)'s awesome work on [`bookdown`](https://github.com/rstudio/bookdown) and [`blogdown`](https://github.com/rstudio/blogdown) packages, but the figures are nested too deep. I just want to put all figures under `static/figures`.

After a bit of digging, [I managed to do this](https://github.com/rbind/daijiang/blob/master/R/build_one.R). The main trick is to add a `knitr` setup chunk to the Rmd file, and then parse it with `blogdown::render_page()`, based on [Yihui's set up](https://github.com/rbind/yihui/tree/master/R). If a post does not have any figures, it will pass the first step and go directly with `blogdown::render_page()`. I did not look through all functions available from the `blogdown` package. But I am sure there must be a better way to do this. Anyway, I get what I want at this moment.

************

## Citations

For citations, put the bibtex file in the same folder as the post, and then add `bibliography: ref.bib` in the yaml. You can even define the citation styles via `csl: url_of_csl_file` in the yaml.^[A local file in the same folder will work too.] Thousands of csl files are available at [Github CSL repository](https://github.com/citation-style-language/styles). Go and find one you like and paste the url in the yaml. 

Testing paragraph: Invasion of non-native species, one of the most widespread and harmful consequences of global change, is causing worldwide ecosystem degradation and economic loss [@vila2011ecological; @simberloff2013impacts]. 

## Math equations

Here is inline equations $a^2 + b^2 = c^2$; and display equations:

$$f(x)=\frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{(x-\mu)^{2}}{2\sigma^{2}}}$$

## R code chunk

```{r cars}
summary(cars)
```

## Including plots and cross-refer it back

You can also embed plots and cross-refer it with `\@ref(fig:figure-label)`, for example Figure \@ref(fig:pressure):

```{r pressure, fig.cap="Here is figure caption."}
plot(pressure)
```

## Table and cross-reference

You can also print tables and cross-refer it with `\@ref(tab:table-label)`, for example Table \@ref(tab:pressure2):

```{r pressure2}
knitr::kable(head(pressure), caption = "Table legend.")
```

That's it.

Any suggestions to improve this workflow? Comment below or send me a pull request. Thanks.

# References

